Git Learning Notes

### 2014-01-27 ch-moox/moox.tex
moo3 012714

\chapter{Molybdenum Oxides}

@@

\section{Syntheses Methods}
\subsection{literature review}

@@

After least-squares fitting, the coefficients $a$ and $n$ can be used to estimated the scattering in other wavelengths. The fitting of n usually falls between -2 and -4. We examined the t40h line in Fig.~\ref{fig:moabs} and found the scattering part is almost zero. Therefore we did not perform aforementioned fitting. This is not always the case. In chapter on the \ce{WS2} section, we do need to do so.

@@

\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:moind}\includegraphics[width=0.45\textwidth]{n_MoO3}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:mocon}\includegraphics[width=0.45\textwidth]{Graph20}}
\caption[Refractive indices of \ce{MoO3}]{(a) Refractive indices of \ce{MoO3} Dashed line is n along $a$ axis while solid line is along $c$ axis. (b) optical contrast mapping of 1L \ce{MoO3} on \ce{SiO2}-Si. The x axis is \ce{SiO2} thickness, y axis is wavelength.It is assumed that the incident light is polarized along c axis of \ce{MoO3}.}
\label{fig:mofl}
\end{figure}

Fig.~\ref{fig:mocon} illustrates the optical contrast mapping of 1L \ce{MoO3} on \ce{SiO2}-Si when the incident light is polarized along c axis of \ce{MoO3}. One can see that .
The refractive indices of Si and \ce{SiO2} within visible wavelengths and MATLAB source code for optical contrast calculation is included in Appendix.

The dimension and phase of exfoliated \ce{MoO3} is examined using TEM. Fig.~\ref{fig:motem} shows the size of exfoliated \ce{MoO3} is about 500 nm. High-resolution TEM (HRTEM) image was taken to assess the \ce{MoO3}. The clearly resolved lattices indicate high crystal quality of \ce{MoO3}.

@@

@@

As shown in Fig, we found several solid clusters with diameter about 1 $\mu m$ on the top part of long belts. According to the \ce{Na2MoO4}-\ce{MoO3} binary compounds phase diagram, we expect the terminating solid clusters have a Na:Mo ratio close to 0.6. The experimental results match well with this predictions. EDX analysis reveal the presence of Na on the solid cluster but not at about 1$\mu m$ away from previous location.\footnote{the sensitivity of our instrument is estimated to be 1\% atomic leve} Quantitative atomic ratio derived from the solid cluster is not close to the one predicted by phase diagram probably due to the high Mo content in adjacent area. However, XRD examinations on a short time growth sample revealed a possible \ce{Na2Mo4O13} phase(PDF 028-1112), providing an indirection evidence of the droplet composition.

@@

Nanotower is a less common morphology in the structures of nanomaterials.\cite{Kharissova2010} We have not found report on  \ce{MoO3} nanotower structures, although there are several studies on \ce{In2O3},\citep{Jean2010,Yan2007}, GaN\cite{Xiao2012} and ZnO\cite{Zhang2013c}. \citeauthor{Jean2010} investigated the growth mechanism of \ce{In2O3} nanotowers and attributed it to the periodical axial and continuous lateral growth interaction, where the former was first guided by Au-In alloy liquid, and subsequent by self-catalytic In droplets (MP 156C) while the latter due to VS process. In contrast, \citeauthor{Yan2007} observed similar \ce{In2O3} nanotower growth and proposed that the axial growth is controlled by Au-catalytic VLS process. \citeauthor{Xiao2012} reported the GaN nanotower grown on Ni-coated Si(111) substrates and explained the growth as asymmetric self-copy process based on VLS mechanism. \citeauthor{Zhang2013c} studied the growth of ZnO nanotower and provided a competitive model between axial and lateral growth controlled by Zn vapor to explain the as-synthesized structures. (When ZnO and carbon mixture was used as source instead of ZnO alone, nanorods array results, presumably due to the stable supply of Zn vapor owing to the gentle carbothermal reduction.) Therefore the fluctuation of reagents is probably responsible for tapering and periodical modification, which is absent in the coin roll style growth of \ce{MoO3} tower on Si. The occasionally observed tapering or enlarging on \ce{MoO3} tower can be attributed to the cooling down growth.  An oxygen regulated growth will be conducted to reveal the role of vapor pressure during the formation of tower.

>>>>

% git version control added 012614
\chapter{Molybdenum Oxides}

@@

\section{Syntheses Methods}
\subsection{literature review}
crystal-chemical principles. Due to the weak cation-oxygen bonding, alkali metal cations only introduce small perturbations into the energies of Mo-O or W-O ensembles in comparison to cations of other elements. And no mixing of vibrations of the cationic sublattices with that of \ce{Mo-O} or \ce{W-O} lattices. So the structural features of \ce{Mo-O} or \ce{W-O} polyhedra are dominating factors affecting the vibration frequencies and thermodynamic values of the molybdates and tungstates.\cite{Fomichev1992}

\begin{table}[htb]
\centering
\caption{Crystal structures of alkali metal molybdates and tungstates}\label{tab:naxmow}
\begin{tabular}{lcr}
\toprule
formula & structure  & remarks  \\
\midrule
\ce{A2O:MO3}\textsuperscript{\emph{a}} & isolated tetrahedral \ce{MO4} anions& \\
\ce{A2O:2MO3} & chain-type anions of \ce{MO4} and \ce{MO6} & \\
\ce{A2O:3MO3} & chain-type anions of \ce{MO5} and \ce{MO6} & \\
\ce{A2O:4MO3} & chain-type anions of \ce{MO6} & \\
\bottomrule

\textsuperscript{\emph{a}} A = Li, Na, K, Rb, Cs; M = Mo, W;
\end{tabular}
\end{table}

Assignment for \ce{A2MO4} is well grounded. Alkali metal cations with octahedral coordination occur below 230 $cm^{-1}$. For \ce{A2M_nO_{3n+1}}, exact assignment is not available yet due to the complicated \ce{MO6} octahedra.

@@

After least-squares fitting, the coefficients $a$ and $n$ can be used to estimated the scattering in other wavelengths. The fitting of $n$ usually falls between -2 and -4. We examined the t40h line in Fig.~\ref{fig:moabs} and found the scattering part is almost zero. Therefore we did not perform aforementioned fitting. This is not always the case. In chapter on the \ce{WS2} section, we do need to do so.

@@

\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:moind}\includegraphics[width=0.45\textwidth]{n_MoO3}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:mocon}\includegraphics[width=0.45\textwidth]{MoO3_1L}}
\caption[Refractive indices of \ce{MoO3}]{(a) Refractive indices of \ce{MoO3} Dashed line is n along $a$ axis while solid line is along $c$ axis. (b) optical contrast mapping of 1L \ce{MoO3} on \ce{SiO2}-Si. The x axis is \ce{SiO2} thickness, y axis is wavelength.It is assumed that the incident light is polarized along c axis of \ce{MoO3}.}
\label{fig:mofl}
\end{figure}

Fig.~\ref{fig:mocon} illustrates the optical contrast mapping of 1L \ce{MoO3} on \ce{SiO2}-Si when the incident light is polarized along c axis of \ce{MoO3}. One can see that there is a pseudo-periodical trend with either wavelength or \ce{SiO2} thickness fixed. The positive extreme occur at around 80nm and 240nm \ce{SiO2} layer, slightly less than the optimum for observing graphene. The refractive indices of Si and \ce{SiO2} within visible wavelengths and MATLAB source code for optical contrast calculation is included in Appendix, with which one can readily evaluate the few layers \ce{MoO3} scenarios and the circumstance when incident light is polarized along a axis.

The dimension and phase of exfoliated \ce{MoO3} is examined using TEM. Fig.~\ref{fig:motem} shows the size of exfoliated \ce{MoO3} is about 500 nm. High-resolution TEM (HRTEM) image was taken to assess the \ce{MoO3} crystallinity. The clearly resolved lattices indicate high crystal quality of these exfoliated \ce{MoO3}.

@@

Nevertheless, identifying these few layer \ce{MoO3} under optical microscope is still difficult due to both the small flake size and low contrast.\footnote{Human eye threshold contrast (contrast sensitivity)$^{-1}$ is about}

@@

As shown in Fig, we found several solid clusters with diameter about 1 $\mu m$ on the top part of long belts. According to the \ce{Na2MoO4}-\ce{MoO3} binary compounds phase diagram, we expect the terminating solid clusters have a Na:Mo ratio close to 0.6. The experimental results match well with this predictions. EDX analysis reveal the presence of Na on the solid cluster but not at about 1$\mu m$ away from previous location.\footnote{the sensitivity of our instrument is estimated to be 1\% atomic level} Quantitative atomic ratio derived from the solid cluster is not close to the one predicted by phase diagram probably due to the high Mo content in adjacent area. However, XRD examinations on a short time growth sample revealed a possible \ce{Na2Mo4O13} phase(PDF 028-1112), providing an indirection evidence of the droplet composition.

@@

### 2014-01-27 foo.tex
foo on develop
moo3 012714

\documentclass[12pt,letterpaper]{article}
\usepackage{listings}
\lstset{
frame = single,
language = bash,
breaklines = true,
postbreak=\raisebox{0ex}[0ex][0ex]{\ensuremath{\color{red}\hookrightarrow\space}}
}

@@

% checkout from github 
git add remote hw https://github.com/qisaiman/hw.git
git fetch hw master or develop 
git push hw master
\end{lstlisting}

Git protocol 9148 port.

@@

\begin{table}
  \caption{Commands}
  \label{tbl:notes}
  \begin{tabular}{ll}
    \toprule
    Command                            & Function \\
    \midrule
    gitk\textsuperscript{\emph{a}}   & Visualization versioning history  \\
    git status\textsuperscript{\emph{b}} & current working flow state \\
    ssh key   & zgcss627\\

>>>>

\documentclass[12pt,letterpaper]{article}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{listings}
\lstset{
frame = single,
language = bash,
breaklines = true,
postbreak=\raisebox{0ex}[0ex][0ex]{\ensuremath{\color{red}\hookrightarrow\space}}
}

@@

% checkout from github 
git add remote hw https://github.com/qisaiman/hw.git
git fetch hw master or develop 
git merge hw/master
git push hw master:master
% or 
git push hw master:hw/master % use my master branch to update remote

% view current remote
git remote -v
% remove origin remote
git remote rm origin

%create a branch develop and switch to it
git checkout -b develop
{some editing }
git commit -m ''
git checkout master 
git merge develop % into current branch 
% inspect the branch status 
git branch --merged % show merged branch 
git branch --no-merge % show unmerged works

% delete a branch
git branch -d develop

\end{lstlisting}

\begin{lstlisting}
% initialization
touch README.md
git init
git add README.md
git commit -m "first commit"
git remote add origin git@github.com:qisaiman/cv.git
git push -u origin master

% view current remote 
git remote -v 
% remove origin remote 
git remote rm origin

% to view current config
git config --list

\end{lstlisting}
Git protocol 9148 port.

@@

\begin{table}[htb]
  \caption{Commands}\label{tbl:notes}
  \centering
  \begin{tabular}{lr}
    \toprule
    Command                            & Function \\
    \midrule
    gitk\textsuperscript{\emph{a}}   & Visualization versioning history  \\
    git status\textsuperscript{\emph{b}} & current working flow state \\
    ssh key   & zgcss627\\
